---
title: "Simulated VaR - Modeling Uncertainty in VaR"

author: "Luis Fernando C Costa"

date: "19/09/2020"

output: github_document
  
---

These codes perform the estimators used to obtain the GARCH (1,1) parameters, as well as calculate the VaR through parametric and Filtered Historical Simulation methods.  

```{r packages, include=FALSE}
library(rugarch)
library(tictoc)
library(parallel)
library(Metrics)
library(Rsolnp)
library(fBasics)
library(pracma)
library(PerformanceAnalytics)
library(zoo)
library(quantmod)
library(resample)
library(gdata)
library(NlcOptim)
```
### loading the estimators
```{r loading estimators}

source("Estimators-Modeling-Uncertainty-in-VaR.r")

```

### VaR function 

VaRf performs the one-step ahead Value-at-risk forecast
Inputs:

1. param is a vector with the estimated parameters (omega, alpha beta, shape) 
 obtained through the estimators : GQML,STD, NG, Rank etc..
2. X is the time series (returns).
3. dis is the distribution. 

The function returns a list with 10 elements:

1. (from column 1 to 4) (VaRa) - parametric VaR with 0.05, 0.01, 0.005 and 0.001 risk level.
2.  One-day-ahead conditional sd forecast (Fsigma)
3.  The last observation of the standardized residuals (z): useful to estimate 
the shape parameter.
4. (from column 7 to 10) (VaRz) - FHS (Filtered historical simulation) VaR with 0.05,
0.01, 0.005 and 0.001 risk level.

```{r VaRf, echo=TRUE}

VaRf<- function(param, X, dis) {
  
  
  spec = ugarchspec(variance.model = list(model = "sGARCH"),
                     mean.model=list(armaOrder=c(0,0), include.mean=FALSE),
                     distribution.model = dis)
  
  spec@model[["fixed.pars"]]<-param
  
  #One-step-ahead cond. sd. forecast
  
  H<-ugarchforecast(spec, X, n.ahead = 1)
  H_1<-as.numeric(H@forecast$sigmaFor)
  sigma<-H@model[["modeldata"]][["sigma"]] #estimated conditional sd.
  z<-X/sigma
  
  
  #Estimating the shape parameter of a STD or a GED dist.
  #We set shape=40 for a normal (it does not affect the normal VaR estimation)
  
  if(dis=="norm"){
    shape=40
  }else{
    shape=spec@model[["fixed.pars"]][["shape"]]
  }
  
  #Parametric VaR: 5%, 1%, 0.5% and 0.1% level of significance:
  
 # Considering the shape parameter estimated previously.
  
  VaR5a<-as.numeric(H_1*(qdist(distribution = dis, mu=0, sigma=1, 
                        p=0.05, shape=shape)))
  
  VaR1a<-as.numeric(H_1*(qdist(distribution = dis, mu=0, sigma=1,
                        p=0.01, shape=shape)))
  
  ans<-list(
    
    VaR5a=VaR5a,
    
    VaR1a=VaR1a,
    
    FSigma=H_1,
    
    )
  
  return(ans)
  
  }
```

### Simulated returns

This function simulates a GARCH(1,1) process and returns.
The inputs are: 

1. n (number of observations - 3500 is fixed)
2. no_simulations
3. df=degrees of freedom (Student-t dist - min is 3)
5. distribution of the processes innovations dis="std" or "ged".
6. w=estimation window (we use 250, 500, 1000 and 2500)

Besides these inputs it is necessary to inform the parameters previously: omega, alpha and beta.

This function returns a list of 13 elements:

1.  Simulated returns (R)
2.  Simulated conditional standard deviation (V)
3.  Simulated standardized residuals (Z)
4.  Shape parameters of the simulations
5.  VaR5a parametric -true VaR with alpha=0.05
6.  VaR1a parametric true VaR with alpha=0.01
7.  VaR5t parametric true VaR with alpha=0.005
8.  VaR1t parametric true VaR with alpha=0.001
9.  VaR5z empirical -true VaR with alpha=0.05
10. VaR1z empirical true VaR with alpha=0.01
11. VaR5tz empirical true VaR with alpha=0.005
12. VaR1tz empirical true VaR with alpha=0.001
13. rea - realized returns (the last 1000 observations of returns to evaluate the VaR)

```{r Function Simulated Returns, echo=TRUE}


returns<-function(n,no_simulations,df,dis){
  
 spec=ugarchspec(variance.model=list(model="sGARCH", garchOrder=c(1,1)),
                  mean.model=list(armaOrder=c(0,0), include.mean=FALSE), 
                  distribution.model=dis, fixed.pars=list(mu=0,
                  omega=omega, alpha1=alpha, beta1=beta,  skew= sk, shape=df))
  
  path.sgarch = ugarchpath(spec, n.sim = n, n.start=1001,
                m.sim = no_simulations, rseed = 42)#3   #3489 #rseed=589, 3478
  
  #Burn-in sample -> n.start=1001
  
  R<-path.sgarch@path[["seriesSim"]]
  
  V <- path.sgarch@path$sigmaSim
  
  out<-list(R = R, V = V )
  
  return(out)
}
# 0.01,0.09, 0.9 df3  seed 42
# 0.01,0.09, 0.9 df7  seed 52
# 0.01,0.1, 0.8 df3  seed 62
# 0.01,0.1, 0.8 df7  seed 72

```

### Process setting
```{r Process setting, echo=TRUE}

omega<-0.01  
alpha<-0.09 
beta<-0.9 
True_parameters<-c(omega, alpha, beta)
dis="std"   # distribution 
sk<-1 # 1 = no skewness 
n <-3500 # is the number of observations(this number is fixed)
no_simulations <-100
df=3 # degrees of freedom 3 8 
w<-250 #estimation window (250, 500, 1000 and 2500)
```

### Simulating the processes 
We use estimation window with length = "w" to forecast the 1000 next days, through a 1-step ahead rolling window scheme
```{r Simulation, eval=FALSE, echo=TRUE}

tic()
data <- returns(n, no_simulations,df, dis)
toc()
out<-1000 # days ahead to forecast(fixed)
 
#rea<-unlist(data$R[,]) # rea (realised - out-of-sample)
#X<-R[1:(nrow(R)-1),] #Matrix of returns up to (n-1)
#X1 = data$R
```

### Defining the estimation window
```{r Defining the estimation window, eval=FALSE, echo=TRUE}

w = 250 # 250, 500, 1000, 2500

X <- data$R[2251:3500,]

rea <- X[251:(length(X[,1])),]   # rea (realised - out-of-sample)

X<-X[1:(nrow(X)-1),] #Matrix of returns up to (n-1)




```
